### 2015-05-17 writing/SNLI paper/corpus.tex
Paper push &c.

@@

quote from SICK paper \cite{marelli2014sick}:

@@

\paragraph{validation}

The majority of the sentence pairs in the corpus have not been reviewed by anyone since their construction as part of the data collection Mechanical Turk task, except to remove blank responses and responses where the original author flagged the source caption for review. However, in order to measure the accuracy of our corpus, and in order to improve the quality of our test and development sets, we did perform an additional round of validation for TODOk examples.

This validation phase is not fundamentally different from the Mechanical Turk labeling task used for the SICK entailment data: we present workers with pairs of sentences (in our case, in batches of five per screenfull), and ask them to choose a single label for each pair. We supplied each pair to four annonators, yielding five labels per pair including the label used by the original composer of the pair.

@@

\begin{table}
\center
  %\setlength{\tabcolsep}{15pt}
  %\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{l l} 
    \toprule
Training pairs &  550,157\\
Dev pairs &  10,000\\
Test pairs &  10,000\\
Total & 570,157\\
\midrule
L. mean token count & 14.1\\
R. mean token count & 8.3 \\
\midrule
L. complete sentences & 70.2\%\\
R. complete sentences & 75.4\%\\
    \bottomrule
  \end{tabular}
\caption{\label{b-table}Key statistics for the raw sentence pairs. Since the left and right halves of each pair were collected separately, we report statistics for both.} 
\end{table}

\begin{table}
\center
  %\setlength{\tabcolsep}{15pt}
  %\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{l l} 
    \toprule
Validated pairs \& 53,852
Consensus label $\ne$ original label \& 8.5\%
No consensus label $\ne$ \& 2.1\%
Unanimous consensus \& 57.7\%

    \bottomrule
  \end{tabular}
\caption{\label{b-table}Key statistics for the validated sentence pairs.} 
\end{table}

Total multiply annotated pairs: 53852
Fraction where gold != original or no gold label: 0.0851593255589
Fraction where gold != original: 0.0645844165491
Fraction with no gold label: 0.0205749090099
Fraction with unanimous agreement: 0.576561687588
%% annotator agreement with gold labels: 0.889371871517
%% annotator agreement with original labels: 0.855424084595

\begin{table}
\center
  %\setlength{\tabcolsep}{15pt}
  %\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{l lll} 
    \toprule
\textbf{Label} & \textbf{Train} & \textbf{Dev} & \textbf{Test}\\
\midrule
\ii{entailment} &33.3 & 33.3 & 33.0 \\
\ii{neutral} & 33.2 & 32.7 & 32.5 \\
\ii{contradiction} & 33.3 & 32.2 & 32.8 \\
no gold label & 0.1 & 1.8 & 1.8 \\
\bottomrule
  \end{tabular}
  % Dist. of each label in each data set.
\caption{\label{b-table}Frequency (\%) of each label in the corpus. Note that unlabeled examples are omitted in standard evaluations.} 
\end{table}

@@

\paragraph{data partition}

\paragraph{simple baselines}

MFC

BLEU

Summing + NN

>>>>

\subsection{Grounding with imagined images}

Quote from SICK paper \cite{marelli2014sick}:

\subsection{Data collection}

\subsection{Data validation}

\subsection{Statistics}

@@

@@

\paragraph{Validation}

The majority of the sentence pairs in the corpus have not been reviewed by anyone since their construction as part of the data collection Mechanical Turk task, except to remove blank responses and responses some pairs which the original author flagged for review. However, in order to measure the quality of our corpus, and in order to construct maximally useful testing and development sets, we did perform an additional round of validation for about 54k examples.

This validation phase is not fundamentally different from the Mechanical Turk labeling task used for the SICK entailment data: we present workers with pairs of sentences (in our case, in batches of five at a time), and ask them to choose a single label for each pair. We supplied each pair to four annonators, yielding five labels per pair including the label used by the original composer of the pair.

The results of this validation process are summarized in Fig.~\ref{validation-stats}. For each pair that we validated, we chose a gold label. If any one of the three labels was chosen by at least three of the five annotators, that label is the gold label. If there was no such consensus, which occurred in about 0.2\% of cases, we chose the label `-'. While these unlabeled examples are included in the corpus distribution, they are unlikely to be helpful for the core classification task of NLI, and we

@@

\begin{figure}
\center
\includegraphics[width=3.05in]{length_dist}
    % From 1.0rc2
\caption{\label{b-table}The distribution of sentence length.} 
\end{figure}

\begin{table}
\center
  %\setlength{\tabcolsep}{15pt}
  %\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{l l} 
    \toprule
Pairs in corpus & 570,157\\
Training pairs &  550,159\\
Dev pairs &  9,999\\
Test pairs &  9,999\\
\midrule
Premise mean token count & 14.1\\
Hypothesis mean token count & 8.3 \\
\midrule
Premise complete sentences & 70.2 ??\%\\
Hypothesis complete sentences & 75.4 ??\%\\
    \bottomrule
  \end{tabular}
    % From 1.0rc2
\caption{\label{validation-stats}Key statistics for the raw sentence pairs. Since the two halves of each pair were collected separately, we report statistics for both.} 
\end{table}

\begin{table}
\center
  %\setlength{\tabcolsep}{15pt}
  %\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{l l} 
    \toprule
Validated pairs & 53,852\\
gold label $\ne$ original label & 8.5\%\\
Unanimous gold & 57.7\%\\
No gold (no 3 labels match) & 2.1\%\\
Label $=$ gold & 88.9\%\\
Label $=$ original author's label & 85.5\%\\
    \bottomrule
  \end{tabular}
    % From 1.0rc2
\caption{\label{b-table}Key statistics for the validated sentence pairs.} 
\end{table}

\begin{table}
\center
  %\setlength{\tabcolsep}{15pt}
  %\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{l lll} 
    \toprule
\textbf{Label} & \textbf{Train} & \textbf{Dev} & \textbf{Test}\\
\midrule
\ii{entailment} &33.3 & 33.4 & 33.3 \\
\ii{neutral} & 33.2 & 33.2 & 33.2 \\
\ii{contradiction} & 33.3 & 33.2 & 33.3 \\
- (no consensus) & 0.2 & 0.2 & 0.2 \\
\bottomrule
  \end{tabular}
  % From 1.0rc2
\caption{\label{b-table}Frequency (\%) of each label in the corpus. Note that examples without gold labels are omitted in standard evaluations.} 
\end{table}

@@

\paragraph{Partition} We distribute the corpus with a pre-specified train/test/development split. The test and development sets contain 10k examples each. Each original ImageFlickr caption occurs in only one of the three sets, and all of the examples in the test and development sets have gone through validation.

\paragraph{General evaluation standards}
While we hope that the corpus will be valuable in a variety of ways, we encourage researchers working on tools for semantic representation and inference to evaluate on our data in a uniform way: training on only the (parsed and/or unparsed) sentences included in the training set, and doing final evaluations on only the subset of the test set for which there are single gold labels.
